Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-26 Scripts/Initial_Analysis.Rmd
Code for first analisis done

mclapply(
  spp_list[1],
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensamble_list = ensamble_list[1],
  path = DBEM_path,
  neighbours = Neighbours
)

@@

@@

>>>>

mclapply(
  spp_list,
  EstPropChange,
  year <- year_df,
  data_type <- "Catch",
  ensamble_list = ensamble_list,
  path = DBEM_path,
  neighbours = Neighbours
)

@@

# Hall 1000 ran it in 5.33 hours

@@

# Results

## Functions and Data needed

### Fun `SummaryProp`

This function estimates the total change in MCP proportion of each species for each EEZ. It looses the connection with neighbours as you only know for x species houw much is the proportion changing.

```{r fun_SummaryProp, eval = T, echo =F}

  SummaryProp <- function(taxon_key){

    # Reads taxon data
    proportion_data <- fread(paste(result_path,"Proportion/","proportion_",taxon_key,".csv", sep=""))

    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensamble_mean,na.rm=T) # average spp change from all countries sharing
      )

    return(country_summary)
  }

### Fun `EEZProp`

The next step is to summarize all species per eez

```{r fun_EEZProp, eval = T, echo = F}

EEZProp <- function(taxon_list){

 spp <- bind_rows(
   lapply(taxon_list,SummaryProp)
   )

 eez_summary <- spp %>% 
   group_by(eez_name,time_step) %>% 
   summarise(
      min_spp = min(mean_spp),
     max_spp = max(mean_spp),
     sd_spp = sd(mean_spp,na.rm=T), # for some weird reason it wont work if the order is fliped
     mean_spp = mean(mean_spp,na.rm=T)
   ) %>% 
   select(eez_name:max_spp,mean_spp,sd_spp)

 return(eez_summary)

}

taxon_list <- c(600015,600017)
taxons <- c(600004,600004,600015,600017)
x <- NULL
x <- PropChange(taxons)

### Fun `PropChange`

Finally, we estimate the average proportion change of all species within each eez

```{r fun_PropChange, eval = T, echo =F}

PropChange <- function(taxon_list){

 eez <- EEZProp(taxon_list)

 proportion_change <- eez %>% 
   gather("variable","value",min_spp:sd_spp) %>% 
   spread(time_step,value) %>% 
   mutate_at(vars(
     "per_mid" = mid,
     "per_end" = n_end),
            funs(round((((.-historical)/.))*100,2))
   )

 return(eez_summary)

}

## Run Results Analysis

```{r fun_PropChange, eval = T, echo =F}

# Get taxon list
taxon_list <- list.files(paste(result_path,"/Proportion/",sep=""))

# clean names for function
taxon_list <- gsub(".*_","",taxon_list) 
taxon_list <- gsub("\\..*","",species_list)

Restuls <- PropChange(taxon_list)
